Fusing Filters with Integer Linear Programming

### 2014-05-14 2014betterfusionforfilters/section/05-Benchmarks.tex
add dots between coefficients. just slightly easier to read

\begin{tabbing}
MMMMM   \= MMMMMM \= M \= MMMMMM \= M \= MMMMMM \= \kill
Minimise   \> $25 x_{sum1, gts} + 1 x_{sum1,sum2} + 25 x_{sum1, ys2} + 25 x_{gts, sum2} +$ \\
           \> $25 x_{gts, ys1} + 1 x_{sum2, ys1} + 25 x_{ys1, ys2} + $ \\
           \> $ 5 c_{gts} + 5 c_{ys1} + 5 c_{ys2} $\\
Subject to \\
    \> $-5 x_{sum1, gts}$  \> $\le$ \> $\pi_{gts} - \pi_{sum1}$  \> $\le$ \> $5 x_{sum1, gts}$  \\
    \> $-5 x_{sum1, sum2}$ \> $\le$ \> $\pi_{sum2} - \pi_{sum1}$ \> $\le$ \> $5 x_{sum1, sum2}$ \\
    \> $-5 x_{sum1, ys2 }$ \> $\le$ \> $\pi_{ys2 } - \pi_{sum1}$ \> $\le$ \> $5 x_{sum1, ys2 }$ \\
    \> $-5 x_{gts,  ys1 }$ \> $\le$ \> $\pi_{ys1 } - \pi_{gts }$ \> $\le$ \> $5 x_{gts, ys1  }$ \\
    \> $-5 x_{sum2, ys1 }$ \> $\le$ \> $\pi_{ys1 } - \pi_{sum2}$ \> $\le$ \> $5 x_{sum2, ys1 }$ \\
    \> $-5 x_{ys1, ys2  }$ \> $\le$ \> $\pi_{ys2 } - \pi_{ys1 }$ \> $\le$ \> $5 x_{ys1, ys2  }$ \\
\\
    \> $   x_{gts, sum2 }$ \> $\le$ \> $\pi_{sum2} - \pi_{gts }$ \> $\le$ \> $5 x_{gts, sum2 }$ \\
\\
    \>                     \>       \> $\pi_{sum1} < \pi_{ys1}$ \\
    \>                     \>       \> $\pi_{sum2} < \pi_{ys2}$ \\
\\
    \> $ x_{gts,sum2} $    \> $\le$ \> $c_{gts}$ \\
\\
    \> $x_{sum1,sum2}$     \> $\le$ \> $x_{sum1, sum2}$ \\
    \> $x_{sum1, gts}$     \> $\le$ \> $x_{sum1, sum2}$ \\
    \> $x_{sum1, gts}$     \> $\le$ \> $x_{sum1, sum2}$ \\
\end{tabbing}
$parents(sum1,sum2)  = \{(sum1, gts)\}$

>>>>

\begin{tabbing}
MMMMM   \= MMMMMMM \= M \= MMMMMMM \= M \= MMMMMMM \= \kill
Minimise   \> $25 \cdot x_{sum1, gts} + 1 \cdot x_{sum1,sum2} + 25 \cdot x_{sum1, ys2} +$ \\
           \> $25 \cdot x_{gts, sum2} + 25 \cdot x_{gts, ys1} + 1 \cdot x_{sum2, ys1} +$ \\
           \> $ 25 \cdot x_{ys1, ys2} + 5 \cdot c_{gts} + 5 \cdot c_{ys1} + 5 \cdot c_{ys2} $\\
Subject to \\
    \> $-5 \cdot x_{sum1, gts}$  \> $\le$ \> $\pi_{gts} - \pi_{sum1}$  \> $\le$ \> $5 \cdot x_{sum1, gts}$  \\
    \> $-5 \cdot x_{sum1, sum2}$ \> $\le$ \> $\pi_{sum2} - \pi_{sum1}$ \> $\le$ \> $5 \cdot x_{sum1, sum2}$ \\
    \> $-5 \cdot x_{sum1, ys2 }$ \> $\le$ \> $\pi_{ys2 } - \pi_{sum1}$ \> $\le$ \> $5 \cdot x_{sum1, ys2 }$ \\
    \> $-5 \cdot x_{gts,  ys1 }$ \> $\le$ \> $\pi_{ys1 } - \pi_{gts }$ \> $\le$ \> $5 \cdot x_{gts, ys1  }$ \\
    \> $-5 \cdot x_{sum2, ys1 }$ \> $\le$ \> $\pi_{ys1 } - \pi_{sum2}$ \> $\le$ \> $5 \cdot x_{sum2, ys1 }$ \\
    \> $-5 \cdot x_{ys1, ys2  }$ \> $\le$ \> $\pi_{ys2 } - \pi_{ys1 }$ \> $\le$ \> $5 \cdot x_{ys1, ys2  }$ \\
\\
    \> $   x_{gts, sum2 }$ \> $\le$ \> $\pi_{sum2} - \pi_{gts }$ \> $\le$ \> $5 \cdot x_{gts, sum2 }$ \\
\\
    \>                     \>       \> $\pi_{sum1} < \pi_{ys1}$ \\
    \>                     \>       \> $\pi_{sum2} < \pi_{ys2}$ \\
\\
    \> $ x_{gts,sum2} $    \> $\le$ \> $c_{gts}$ \\
\\
    \> $x_{sum1,sum2}$     \> $\le$ \> $x_{sum1, sum2}$ \\
    \> $x_{sum1, gts}$     \> $\le$ \> $x_{sum1, sum2}$ \\
    \> $x_{sum1, gts}$     \> $\le$ \> $x_{sum1, sum2}$ \\
\end{tabbing}
$parents(sum1,sum2)  = \{(sum1, gts)\}$
